cardinalR: Generating interesting high-dimensional data structures

### 2025-05-06 paper-cardinalR.Rmd
Add gen_helicalspiral

>>>>

The `gen_helicalspiral(n, p)` function generates a dataset of $n$ observations forming a helical spiral, embedded in the first four dimensions of a $p$-dimensional space. Additional dimensions (if $p > 4$) are filled with structured noise to mimic high-dimensional complexity.

The first four coordinates follow a $3\text{-}D$ helix with an additional oscillating component. Let $\theta \in [0, \frac{5\pi}{4}]$ be a sequence of angles controlling rotation around a circle.

Cartesian coordinates:
  * $X_1 = \cos(\theta)$: circular trajectory along the x-axis.

  * $X_2 = \sin(\theta)$: circular trajectory along the y-axis.

  * $X_3 = 0.05 \cdot \theta + \varepsilon_3$, with $\varepsilon_3 \sim \mathcal{U}(-0.5, 0.5)$: linear progression (height) with vertical jitter, simulating a helix.

  * $X_4 = 0.1 \cdot \sin(\theta)$: oscillates with $\theta$, representing a periodic "wobble" along the fourth dimension.

This results in a helical spiral winding upward along the third axis, with gentle sinusoidal fluctuation in the fourth dimension.

When $p > 4$, the remaining $p - 4$ dimensions are populated using `gen_noisedims()`. These are independent Gaussian noise dimensions:

$$
X_j \sim \mathcal{N}(0, 0.05^2), \quad j = 5, \dots, p.
$$
